InteroceptionStudy_GPValidation

### 2021-08-24 IAPS_PREPROCESSING_2021.Rmd
Create IAPS_PREPROCESSING_2021.Rmd

# self reports
- New Tas is already scored
- score AQ, etc using https://xavierrg.shinyapps.io/datacleaning

@@

db_selfrep <- read_csv("intero_selrep.csv")
View(intero_selrep)
tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid')

@@

View(tmp.df4_sum_full)
write_csv(tmp.df4_sum_full, 'intero_data_full.csv')

@@

etwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")

>>>>

# self reports
- New Tas is already scored
- use questionnaire scoring 2021
- score AQ, etc using https://xavierrg.shinyapps.io/datacleaning

@@

db_selfrep <- read_csv("intero_selrep.csv")
library(readxl)
db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")
# View(db_self_rep_345_356_final)

db_selfrep$ssid <- as.character(db_selfrep$`Participant No`)
tmp.df4_sum_full$ssid <- as.character(tmp.df4_sum_full$ssid)

tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid')

@@

View(tmp.df4_sum_full)
write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_345_356.csv')

@@
